Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-31 ijar-npb-ms.tex
Fix inequality for half-monotonicity.
Finalised edits to Section 6 -- feel free to roll back any/all of them!

The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
enabling diagnoses of prior-data conflict which is consequential at the system
level, via sets of system reliability functions.

@@

We therefore start by proving the following result, where indices are suppressed for readability.
We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.

@@

If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
Theorem 2 cannot determine stochastic dominance.  The following slightly
more computationally costly Lemma may be able to determine first-order
stochastic dominance in such situations.
\begin{lemma}
  \label{lem:n}
  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
  Then,
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{lemma}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
the entire posterior system reliability function must be optimised to 
find the minima/maxima.
In practise, in the examples to be presented in the sequel, Theorem 
\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
stochastic dominance for the vast majority of time points, $t$,
substantially lowering the computational costs of performing the
minimisation/maximisation involved in finding the sets of system 
reliability functions compared to either numerical optimisation or
an exhaustive grid search (which would get exponentially slower in 
the number of different components).

@@

\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}

In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
%***How to choose the sets of priors for the survival function of type $k$ components,
%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***

As mentioned in Section~\ref{sec:nonparamapproach}, for the actual functioning probabilities $\ptk$
it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***
This naturally translates to conditions on the prior guess for $\ptk$,
such that we propose that 
$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
Due to $s^k_t/n_k$ decrasing in $t$ and the weighted average property of the update step for $\ykt$,
this ensures that 
$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
In a situation where we are quite sure about the functioning probability for low $t$,
but are unsure about what happens for larger $t$ and so want to be maximally cautious for those $t$,
then we can let $\yktzl$ drop to (almost) 0, but $\yktzu$ should not increase.
%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
%If we know, e.g., pretty much what's going on for low $t$
%but want to be much more cautious for high $t$,
%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.

We think it is not advisable to express certainty about expected functioning probabilities
with $\nktz$ bounds that vary strongly over $t$.
%***Better to express certainty of prior guess via $\nktz$ bounds?\\
With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
\begin{itemize}
\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
\end{itemize}
Again, this follows from the weighted average property of $\yktn$;
for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to let them change with $t$ gradually only.

Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
low values for $\nktz$ as compared to the test sample size $n_k$
give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
which means more cautious posterior inferences.
The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
as is clear from Figure~\ref{fig:paramsets} and \eqref{eq:ysetupdate}, the wider the $\nktz$ interval,
the wider $[\yktnl, \yktnu]$ in case of conflict.
So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
while choosing $\nktzu$ with help of the half-width rule as described above.

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions
due to zero arguments for the Beta functions in the denominator of \eqref{eq:LwrSysPost}.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
But it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not bring unintuitive tail behaviour
as some parametric methods do;
there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.

%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Switching to a coarser time grid will waste information from data,
as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
We rather propose to elicit bounds for a subset of ${\cal T}$ only,
and to fill up the time grid with the least committal bounds, i.e.,
taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
and likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
A possible elicitation procedure in this vein could be
to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
filling up the grid as described above accordingly,
and then to further refine the obtained bounds as deemed necessary by the expert.
%`middle' or `typical' $t$,
%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,

@@

  Although there exist parameters for which $\mathcal{L}(\cdot)$ is
  not monotone, it is half-monotone.  That is, $\mathcal{L}(l+1) / \mathcal{L}(l)$ is itself monotone.  For simplicity, write
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} = \frac{(l + \pu)(\el - l)}{(l + \pl)(\eu - l)}
    \quad \mbox{where} \left\{\begin{aligned}
      \pu &= \nu y + s \\
      \pl &= \nl y + s \\
      \eu &= m - 1 + \nu (1 - y) + N - s \\
      \el &= m - 1 + \nl (1 - y) + N - s
    \end{aligned} \right.
  \end{align*}
  Then,
  \begin{align*}
    \frac{\mathcal{L}(l+2)/\mathcal{L}(l+1)}{\mathcal{L}(l+1)/\mathcal{L}(l)} =
    \frac{(\pl + l)(\pu + l + 1)(\el - l - 1)(\eu - l)}
           {(\pl + l + 1)(\pu + l)(\el -
l)(\eu - l - 1)}
    &> 1 \\
    \iff \qquad \frac{\pl + l}{\pu + l} \cdot \frac{\el - l - 1}{\eu - l - 1} 
    &> \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
l}{\eu - l}
  \end{align*}
  But, $\pu > \pl > 0$, $\eu > \el > 0$, $l > 0$, %and Lemma \ref{lm:ineq} (p.\pageref{lm:ineq}) with $\xi=\varepsilon=1$ imply
  so it is trivial to prove
  \[
    \frac{\pl + l}{\pu + l} > \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} > \frac{\el -
l}{\eu - l} \qquad \forall\ l \in \{0,\dots,m\}
  \]
  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone increasing.

>>>>

The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
enabling diagnosis of prior-data conflict which is consequential at the system
level, via sets of system reliability functions.

@@

We therefore start by providing the following result, where indices are suppressed for readability.
We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.

@@

If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
Theorem 2 cannot determine stochastic dominance.  The following Lemma which is slightly
more computationally costly, but still much faster than an exhaustive search, may be able to determine first-order
stochastic dominance in such situations.
\begin{lemma}
  \label{lem:n}
  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
  Then,
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{lemma}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
the entire posterior system reliability function must be optimised to 
find the minima/maxima.
In practise, in the examples to be presented in the sequel, Theorem 
\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
stochastic dominance for the vast majority of time points, $t$,
substantially lowering the computational costs of performing the
minimisation/maximisation involved in finding the sets of system 
reliability functions compared to either numerical optimisation or
an exhaustive grid search (which would get exponentially slower in 
the number of different components).

@@

The result for $\uRsys(\cdot)$ is completely analogous.  It is interesting
to note that if $m_k=1$ the bounds are sharp on stochastic dominance.
In particular, when $m_k=1$, $\yktzl < \frac{s^k_t}{n_k}$ indicates the 
lower bound is not in conflict with the observed data, whilst
$\yktzl > \frac{s^k_t}{n_k}$ is in conflict since the observed
empirical probability of functioning at time $t$ is below the
prior lower bound.  Consequently, note that $\nktzl$ is 
used only when the prior comes into conflict with the data.
Since $\nktz$ controls the prior certainty, this accords with
the intuition that the least certain prior bound is invoked
when in a conflict setting and the more certain prior bound used when the data agrees.

\subsection{Prior parameter choice}
In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We advocate that this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.

As mentioned in Section~\ref{sec:nonparamapproach}, the functioning probabilities $\ptk$
must satisfy $p^k_{t_j} \ge p^k_{t_{j+1}}$.% (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***
This naturally translates to conditions on the prior for $\ptk$,
so that for example 
$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
Because $s^k_t/n_k$ is decreasing in $t$, the weighted average property of the update step in
equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
In situations where one has a high degree of certainty about the functioning probability for low $t$,
but less certainty about what happens for larger $t$,
then one can let $\yktzl$ drop to (almost) 0, but clearly $\yktzu$ should not increase.
%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
%If we know, e.g., pretty much what's going on for low $t$
%but want to be much more cautious for high $t$,
%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.

It is inadvisable to express certainty in the expected functioning probabilities
with $\nktz$ bounds that vary substantially over the range of $t$.
%***Better to express certainty of prior guess via $\nktz$ bounds?\\
With (strongly) differing $\nktz$ bounds, monotonicity of the $\yktn$ bounds cannot be guaranteed.
%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
For example, if $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (meaning there is no prior-data conflict),
then should there be no observed failures in $[t_j, t_{j+1}]$, so that $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
\begin{align*}
  \nzu_{k,t_j} < \nzu_{k,t_{j+1}} \quad&\implies\quad\ynu_{k,t_j} < \ynu_{k,t_{j+1}} \quad\mbox{and} \\
  \nzu_{k,t_j} > \nzu_{k,t_{j+1}} \quad&\implies\quad\ynl_{k,t_j} < \ynl_{k,t_{j+1}}
\end{align*}
Again, this follows from \eqref{eq:nyupdate}, the weighted average property.
It is possible to construct similar examples with regard to the lower bound $\nzl_{k,t_j}$.
Therefore, we advise taking the same $\nktz$ bounds for all $t$ as far as possible.
If they do change, it must be very gradual and we recommend diagnosing 
any problems as above.

Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
low values for $\nktz$ as compared to the test sample size $n_k$
give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values.  Specifically, 
in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
which means more cautious posterior inferences.
The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
as is clear from Figure~\ref{fig:paramsets} and \eqref{eq:ysetupdate}, the wider the $\nktz$ interval,
the wider $[\yktnl, \yktnu]$ in case of conflict.
So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
while choosing $\nktzu$ with help of the half-width rule as described above.

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
However, it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step for $\yktn$ (see Equation~\eqref{eq:nyupdate}),
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not cause unintuitive tail behaviour
as some parametric methods do;
there is no problem, for example, with assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.

%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Switching to a coarser time grid will waste information from data,
as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
In the examples here we elicit bounds for a subset of ${\cal T}$
and fill up the time grid with the least committal bounds, i.e.,
taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
and likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
A possible elicitation procedure in this vein could be
to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
filling up the grid as described above accordingly,
and then to further refine the obtained bounds as deemed necessary by the expert.
%`middle' or `typical' $t$,
%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,

@@

  Although there exist parameters for which $\mathcal{L}(\cdot)$ is
  not monotone, it is half-monotone.  That is, $\mathcal{L}(l+1) / \mathcal{L}(l)$ is itself monotone.  For simplicity, write
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} = \frac{(l + \pu)(\el - l)}{(l + \pl)(\eu - l)}
    \quad \mbox{where} \left\{\begin{aligned}
      \pu &= \nu y + s \\
      \pl &= \nl y + s \\
      \eu &= m - 1 + \nu (1 - y) + N - s \\
      \el &= m - 1 + \nl (1 - y) + N - s
    \end{aligned} \right.
  \end{align*}
  Then,
  \begin{align*}
    \frac{\mathcal{L}(l+2)/\mathcal{L}(l+1)}{\mathcal{L}(l+1)/\mathcal{L}(l)} =
    \frac{(\pl + l)(\pu + l + 1)(\el - l - 1)(\eu - l)}
           {(\pl + l + 1)(\pu + l)(\el -
l)(\eu - l - 1)}
    &< 1 \\
    \iff \qquad \frac{\pl + l}{\pu + l} \cdot \frac{\el - l - 1}{\eu - l - 1} 
    &< \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
l}{\eu - l}
  \end{align*}
  But, $\pu > \pl > 0$, $\eu > \el > 0$, $l > 0$, %and Lemma \ref{lm:ineq} (p.\pageref{lm:ineq}) with $\xi=\varepsilon=1$ imply
  so it is trivial to prove
  \[
    \frac{\pl + l}{\pu + l} < \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} < \frac{\el -
l}{\eu - l} \qquad \forall\ l \in \{0,\dots,m\}
  \]
  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone decreasing.
